An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards

### 2023-08-01 article.tex
start of model comparison subsection

% wHY ARE WE COMPARING MODELS?
% We compare models to see which predictors contributed relatively to each of the models.
% Although the graphs showing yield and value look similar when presented as raw values and as ratios of area. The flow of resource use is inverted.
% Talk about how resources use relates to these graphs.
% Show how regions are almost inverted between avereage value vs yield per area when looking at the maps.
%Although the initial correlation between average sales price and yield was a negative trend (see table 2), these models were able to shed light on several contributing factors to yield and average sales price. Correlation values showed that water and emissions increased with yield but decreased with average sale price (see Table 4). In alternative attempts at models it was found that without the incorporation of GI Region or year the predictions greatly under performed. The possible reason behind this effect was that different strategies are likely employed between different regions, where some regions target the mass production of cheaper grapes over quality. This is most notable when grouping regions by climate, especially when considering GI Regions in the ‘Hot Very Dry’ climate (see Figure 7). The effect of climate when used in models was not more significant than the more granular use of GI regions. The interaction between year and GI Region likely accounted for localised events such as bushfires, which would be impactful, but only at a local level in both time and space.
  \label{tab:kfold}
  \caption{Model validation using k-fold cross validation, for 10 folds repeated 100 times.}
  \begin{tabular}{@{}cccc@{}}
    \textbf{} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Mean\\ Squared Error\end{tabular}} & \textbf{R2} & \textbf{\begin{tabular}[c]{@{}c@{}}Mean Average \\ Error\end{tabular}} \\ \midrule
    \textbf{Model 1} & 3.087E-01 & 9.045E-01 & 2.165E-01 \\
    \textbf{Model 2} & 5.104E-01 & 7.409E-01 & 3.493E-01 \\
    \textbf{Model 3} & 1.652E-01 & 9.723E-01 & 1.008E-01 \\
    \textbf{Model 4} & 2.235E-01 & 9.500E-01 & 1.279E-01 \\ \bottomrule
To validate the performance of these models k-fold cross validation was used. This was done using 10 folds, $k=10$, repeated 100 times. The models performed similarly to their original counter parts (see Table \ref{tab:kfold}).
\section{Discussion}
% We want to compare how much influence each variable has on the model!
% This is prior to postulating about the why these variables matter, or have so much influence.
% A table will help to compare the continuous variables, the others are done in the violin plot.
% What is this below paragraph?
%The correlation between average sales price and yield was a negative trend (see table 2); the contributing factors to yield and average sales price was ???. Correlation values showed that water and emissions increased with yield but decreased with average sale price (see Table 4).
In alternative attempts at models it was found that without the incorporation of GI Region or year the predictions greatly under performed. The possible reason behind this effect was that different strategies are likely employed between different regions, where some regions target the mass production of cheaper grapes over quality. % ALSO THAT CATASTROPHES HAPPEN EVEN ON SMALL SCALES THis needs to be tied up better.

>>>>

% Why compare models?

Directly comparing response variables, how value changes with yield, also allows an indirect comparison of resource use. We do this through using the known relationships of the variables to their predictors. These relationships are described by the coefficients, and as the predictors are known to have a strong positive correlation, they will increase together. Resource use is described by the predictor variables (through water used and scope 1 emissions), we can observe these response variables somewhat interchangably with the predictors - although caution should be taken to look at them skeptically and through the lens of their appropriate coefficients. It is important to also consider the interactions of these variables, especially when comparing response variables that are a ratio of area.
%
Although it is adhoc, we also know that each of these predictors are positively correlated when logarithmically transformed, making it likely that the predictors will increase together - although not necessarily at the same rate. Observing Figure \ref{fig:yield_vs_value} shows a predictable convergence towards the mean of 0, with trends appearing in almost stratified lines. These linear formations are caused by regional trends, with some regions being more predictable than others, such as the the 'Hot' regions.
\newline
Comparing Figure \ref{fig:yield_vs_value} to Figure \ref{fig:yield_vs_value_area} shows similar trends. However, a not so obvious difference is that the same vineyards (or graphed points) are dispersed differently. In many cases these graphs are closer to mirror images of each other; this is more visible when comparing regional averages of these response variables, see Figure \ref{fig:map}. 
We can use the response variables relationship to its predictors to compare how resource use changes 
Knowing the response variables relation to resource use

%We compare models to see which predictors contributed relatively to each of the models.
%
% Although the graphs showing yield and value look similar when presented as raw values and as ratios of area. The flow of resource use is inverted.
% Talk about how resources use relates to these graphs.
%
% Show how regions are almost inverted between avereage value vs yield per area when looking at the maps.
%
%
%Although the initial correlation between average sales price and yield was a negative trend (see table 2), these models were able to shed light on several contributing factors to yield and average sales price. Correlation values showed that water and emissions increased with yield but decreased with average sale price (see Table 4). In alternative attempts at models it was found that without the incorporation of GI Region or year the predictions greatly under performed. The possible reason behind this effect was that different strategies are likely employed between different regions, where some regions target the mass production of cheaper grapes over quality. This is most notable when grouping regions by climate, especially when considering GI Regions in the ‘Hot Very Dry’ climate (see Figure 7). The effect of climate when used in models was not more significant than the more granular use of GI regions. The interaction between year and GI Region likely accounted for localised events such as bushfires, which would be impactful, but only at a local level in both time and space.
\subsection{Model Validation}
\begin{table}[]
  \label{tab:kfold}
  \caption{Model validation using k-fold cross validation, for 10 folds repeated 100 times.}
  \resizebox{\textwidth}{!}{
  \begin{tabular}{@{}cccc@{}}
    \toprule
    \textbf{} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Mean\\ Squared Error\end{tabular}} & \textbf{R2} & \textbf{\begin{tabular}[c]{@{}c@{}}Mean Average \\ Error\end{tabular}} \\ \midrule
    \textbf{Model 1} & 3.087E-01 & 9.045E-01 & 2.165E-01 \\
    \textbf{Model 2} & 5.104E-01 & 7.409E-01 & 3.493E-01 \\
    \textbf{Model 3} & 1.652E-01 & 9.723E-01 & 1.008E-01 \\
    \textbf{Model 4} & 2.235E-01 & 9.500E-01 & 1.279E-01 \\ \bottomrule
    \end{tabular}
  }
  \end{table}
To validate the performance of these models k-fold cross validation was used. This was done using 10 folds, $k=10$, repeated 100 times. The models performed similarly to their original counter parts (see Table \ref{tab:kfold}).
\section{Discussion}
% We want to compare how much influence each variable has on the model!
% This is prior to postulating about the why these variables matter, or have so much influence.
% 
% A table will help to compare the continuous variables, the others are done in the violin plot.
%
% What is this below paragraph?
%The correlation between average sales price and yield was a negative trend (see table 2); the contributing factors to yield and average sales price was ???. Correlation values showed that water and emissions increased with yield but decreased with average sale price (see Table 4).
%
In alternative attempts at models it was found that without the incorporation of GI Region or year the predictions greatly under performed. The possible reason behind this effect was that different strategies are likely employed between different regions, where some regions target the mass production of cheaper grapes over quality. % ALSO THAT CATASTROPHES HAPPEN EVEN ON SMALL SCALES THis needs to be tied up better.
%
